---
title: "DA"
output: html_document
---

```{r}
library("tidyverse")
```

```{r}
file1 <- readxl::read_excel("questionnaire 1.xlsx") 
file2 <- readxl::read_excel("questionnaire 2.xlsx")
file3 <- readxl::read_excel("questionnaire 3.xlsx")
```


#This creates a function called "calculatemean", which transforms the data from wide format to long; groups by the question and then calculates the mean response per question. The function requires a table (x) to run
```{r}

calculatemean <- function(x) {
  x %>%
  gather("q", "score", 3:130) %>%
  group_by(q) %>%
  summarise(mean = mean(score, na.rm = TRUE))
}

```


#This creates 3 tables with the mean responses per question for the 3 questionnaires
```{r}
mean1 <- calculatemean(file1)

mean2 <- calculatemean(file2)

mean3 <- calculatemean(file3)
```


#Now that the questionnaire data is in long format the 3 questionnaires can be joined according to the question. Afterwards, the mean and the sd are calculated across the 3 questionnaires
```{r}

tog <- full_join(mean1, mean2, by = "q") %>% 
  full_join(mean3, by = "q") %>%
  gather("quest", "score", 2:3) %>%
  group_by(q) %>%
  summarise(mean = mean(score, na.rm = TRUE))
```


#this is a graph of the distribution 
```{r}
tog %>% ggplot(aes()) + geom_density(aes(mean))
```

#selects the least familiar items and clculates mean and sd
```{r}
bottom32 <- tog %>%
  arrange(mean) %>%
  top_n(-32, mean)

meanb32<- bottom32 %>%
  summarise(MEAN = mean(mean), 
            SD = sd(mean))
```

#Selects the most familiar items
```{r}
top32 <- tog %>%
  arrange(desc(mean)) %>%
  top_n(32, mean)

meant32<- top32 %>%
  summarise(MEAN = mean(mean), 
            SD = sd(mean))
```


